### 2021-08-12 paper/paper.tex
Update paper/paper.tex
Co-authored-by: Michael Schlottke-Lakemper <michael@sloede.com>

Instead of providing only the very basic discretization ingredients, as with
other open source libraries for PDEs, \trixi also includes some widely used
physical systems as well as analysis routines, such as computation of the integrated kinetic energy
for the compressible Euler equations,
to make it easier to use. Nevertheless, users are not restricted
to the physics models bundled in \trixi. To set up a new type of \lstinline{equations},
it is only necessary to create an appropriate \lstinline{struct} containing all
parameters and to implement pointwise operations such as the calculation of
the fluxes $f^j$ in \eqref{eq:hcl} or two-point numerical fluxes. Due to the Julia language
design with just-ahead-of-time compilation, these fluxes can be inlined into the
library functions of \trixi. Thus, the physics can be separated completely from
the \lstinline{solver} but remain computationally efficient. In particular, this allows
a user to reuse the same numerical fluxes for discontinuous Galerkin methods, finite
difference methods, and variants of finite volume methods.
And even if a new feature requires modifications to methods provided by \trixi: Due to favoring
simplicity over abstractions in the code, it remains comparatively straightforward to modify
existing implementations.

>>>>

Instead of providing only the very basic discretization ingredients, as with
other open source libraries for PDEs, \trixi also includes some widely used
physical systems as well as analysis routines, such as computation of the integrated kinetic energy
for the compressible Euler equations,
to make it easier to use. Nevertheless, users are not restricted
to the physics models bundled in \trixi. To set up a new type of \lstinline{equations},
it is only necessary to create an appropriate \lstinline{struct} containing all
parameters and to implement pointwise operations such as the calculation of
the fluxes $f^j$ in \eqref{eq:hcl} or two-point numerical fluxes. Due to the Julia language
design with just-ahead-of-time compilation, these fluxes can be inlined into the
library functions of \trixi. Thus, the physics can be separated completely from
the \lstinline{solver} but remain computationally efficient. In particular, this allows
a user to reuse the same numerical fluxes for discontinuous Galerkin methods, finite
difference methods, and variants of finite volume methods.
And even if a new feature requires modifications to methods provided by \trixi: Due to favoring
simplicity over excessively generic code, it remains comparatively straightforward to modify
existing implementations.
